---
title: "Twitter Data Analysis with Functional Programming"
author: "Anwesha Guha"
date: "5/15/2022"
output: html_document
---

RQ: Does sentiment 

### STEP 1: Get Data from Twitter API**

[insert description about process]
[include some relevant links]

* [How to Get Twitter Data Using API, R bloggers](https://www.r-bloggers.com/2022/03/how-to-get-twitter-data-using-r/)
* [A Guide to Analysing Tweets with R](https://towardsdatascience.com/a-guide-to-mining-and-analysing-tweets-with-r-2f56818fdd16)

[none of the code here is run due API restrictions]

**1.1: Set up Dev account in Twitter**
```{r eval=FALSE, echo=TRUE}
api_key <- "XXXXXX"

api_key_secret <- "XXXXX"

access_token <- "XXXXXX"

access_token_secret <- "XXXXX"

bearer_token <- "XXXXXXXX"
```

```{r eval=FALSE, echo=TRUE}
library(rtweet)
token <- create_token(
  app = "r-program-project",
  consumer_key = api_key,
  consumer_secret = api_key_secret,
  access_token = access_token,
  access_secret = access_token_secret)
```

**1.2: Save the data you are interested in**

I am looking at the hashtag "CRT" or culturally relevant pedagogy. Note: the Twitter API only returns tweets from the last 6-9 days. As a result, the 18000-tweet request was not met; only 1567 tweets exist for that time window.

If you would like more comprehensive coverage, you can apply on the developer website -- though more project details will be required. I will keep the limited number for the sake of this tutorial.

```{r eval=FALSE, echo=TRUE}
crt_tweets <- search_tweets("#CRT", 
                    n = 18000, 
                    include_rts = FALSE)
```
Anisha: May want to comment out 

```{r eval=FALSE, echo=TRUE}
write_csv(crt_tweets, "~/Documents/r_projects/edld653-22/fp_collab/fp-tutorials/data/crt_tweets.csv")
```

### STEP 2: Data cleaning and manipulation

I'll go ahead and load relevant libraries and the csv file created from Step 1 here. 

```{r}
library(pacman)
library(readr)
library(textdata)
p_load(httr, jsonlite, tidyverse, rtweet)
```

Anisha: This may not be correct directory for everyone. I manually read csv from data folder

```{r}
crt_tweet <- read_csv("~/Documents/r_projects/edld653-22/fp_collab/fp-tutorials/data/crt_tweets.csv")
```

**Explore source variable**

```{r}
table(crt_tweet$source)
```

```{r}
crt_tweet <- crt_tweet %>% 
  mutate(source2 = case_when(
    source %in% c("Twitter for Android", "UberSocial for Android") ~ "Android Device",
    source %in% c("Tweetbot for iΟS", "Twitter for iPad", "Twitter for iPhone", "Twitter for Mac") ~ "Apple Device",
    source %in% c("Twitter Web App") ~ "Web App",
    source %in% c("counterganda") ~ "Counterganda", #kept this separate since this was so large
    TRUE ~ "Other"
  ))
```

Better variable to work with:
```{r}
table(crt_tweet$source2)
```

Say we wanted to create models for each of these groups. One way could be to create a dataframe for each group and fit a linear model. 

```{r}
twt_split <- crt_tweet %>% 
  split(crt_tweet$source2)
```

Anisha: What variables do you want to model? Since you already have the data split by source2, source2 will have the same value for all data points in each model. If you want the relationship between favorite_count and source2, I'm not sure why you need to split the data.

```{r}
posslm1 = possibly(.f = lm, otherwise = "Error")

map(twt_split, ~posslm1(favorite_count ~ source2, data = .x) )

```

```{r}
safelm = safely(.f = lm)
map(twt_split, ~safelm(favorite_count ~ source2, data = .x) )
```
^^ I know these above are more artificial uses, but I am still getting errors in running this code. I can't seem to extract x = source2 and y = favorite_count

* idea from [here](https://www.r-bloggers.com/2020/08/handling-errors-using-purrrs-possibly-and-safely/)


**Set up sentiment analysis**

```{r}
library(tidytext)
sentiment <- crt_tweet[,3:5] %>% unnest_tokens(output = 'word', input = 'text')
```

```{r}
sentiment_dataset <- get_sentiments("afinn")
sentiment_dataset <- arrange(sentiment_dataset, -value)

#merge
sentiment <- merge(sentiment, sentiment_dataset, by = 'word')

#clean
sentiment$word <- NULL
sentiment$screen_name <- NULL

#get nearest hour of time for plot
sentiment$hour <- format(round(sentiment$created_at, units="hours"), format="%H:%M")
```

```{r}
search_term <- "#CRT"
pivot <- sentiment %>%
  group_by(hour) %>%
  summarise(sentiment = mean(value))

#plot
ggplot(pivot[-1,], aes(x = hour, y = sentiment)) + 
  geom_line(group = 1) + 
  geom_point() + 
  theme_minimal() + 
  labs(title = paste0('Average sentiment of tweetings mentioning "',search_term,'"'),
       subtitle = paste0(pivot$hour[2],' - ',pivot$hour[nrow(pivot)],' on ', format(sentiment$created_at[1], '%d %B %Y')),
       x = 'Date', 
       y = 'Sentiment', 
       caption = 'Source: Twitter API')
```

[Next step: do sentiment graphs by group]

Sentiment analysis tutorial for reference: [here](https://rforjournalists.com/2019/12/23/how-to-perform-sentiment-analysis-on-tweets/)
