---
title: "data_viz_function"
author: "Manuel Vazquez Cano"
date: "5/1/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
```

## Introduction 

This tutorial will walk through an applied example to show how to simulate survey data
and create a function to graph survey data using divergent bar charts. Creating this 
function would allow the user to graph survey data to any of their liking!

## Simulating data

We begin by simulating some survey data. We will simulate responses to 5 questions that 
use a likert item with a scale of one to four. To ease the simulation of the data, we 
will create a function to generate this data. The function has 5 formals or arguments:
  1. max - An integer that represents the maximum of the likert scale. Since the items we are developing
  are on a 4 point scale, then we will add 4. If we wanted to simulate items on a 7 point
  scale, then we would add a 7 to this argument. 
  2. n - An integer that represents the total number observations that the user wishes to generate
  3. weights - A list of weights that the user specifies to influence the frequency of certain responses.
  The length of the vector should be equal to the max.
  4. levels - A numeric vector that lists the numeric number tied to each response. It should start 
  with 1 and end with the max number specified.
  5. labels - A character vector with the labels attached to the numeric values.
  
The function below also provides an error message in case certain formals are not specified correctly. 
```{r simulate}

# This is how I am generating data without a loop. I can loop the sample specification
# across 5 variables and vary the probability wieghts. Parallel looping?

likert_sim <- function(max, n, weights, levels,labels) {
  if ((length(levels) == length(labels)) & (length(weights) == max))  {
  factor(sample(1:max, n, replace = TRUE, prob = weights),
         levels = levels,
         labels = labels)
  } else {
  stop("Are the length of your labels, levels, or weights equal to the likert item specified? ",  
          " The scale is on a ", max, " point likert item scale. Did you add sufficient arguments?  ",
         ", Number of weight arguments added was ",length(weights),
         ", Number of labels arguments added was ", length(labels),
         ", Number of level arguments added was, ", length(levels))
  }
}

```

Using this function, we simulate the data for five questions which we call q1... to q5. 
The sample scale we will simulate will be a 4 point agreement scale ranging from strongly 
disagree to strongly agree. Before running the function, we define the levels and the labels. 
Again, the lengths of each of these vectors should be similar.

```{r }
levels <- c(1,2,3,4)
labels <- c("Strongly disagree", "Disagree", "Agree", "Strongly agree")

```

Next, we use the levels and labels vectors defined above and plug those in to the function. 
Again, we generate 5 simulated responses with varying weights. 

Note to peer reviewer: Ideas how to put this in a function format?

I'm not sure about a function, but this could work to avoid repetitive code

```{r peer review Anisha}
allWeights <- matrix(c(.20,.30,.25,.25,
                    .10,.50,.15,.25,
                    .25,.10,.50,.15,
                    .30,.30,.10,.30,
                    .39,.45,.15,.10),
                  nrow=5,ncol=4,byrow=TRUE)

allQ <- map(1:5, ~likert_sim(4, 250, allWeights[.x,], levels, labels))

```

```{r }
q1 <- likert_sim(4,250, c(.20,.30,.25,.25),levels,labels)
q2 <- likert_sim(4, 250, c(.10,.50,.15,.25),levels,labels)
q3 <- likert_sim(4, 250, c(.25,.10,.50,.15), levels,labels )
q4 <- likert_sim(4, 250, c(.30,.30,.10,.30), levels,labels)
q5 <- likert_sim(4, 250, c(.39,.45,.15,.10), levels,labels)

```

After we simulate this data, we bind it together into a data frame and generate a random
respone ID. The data is now ready to be graphed!

```{r }
surveydf <- cbind(q1,q2,q3,q4,q5) %>%
  as_tibble() %>%
  mutate(id = ids::random_id(250, 4))

```

## Create a function to graph the data

Now that we have the data simulated, we are ready to graph. In order to create a divergent
horizontal bar chart, we need to take on two steps. First, we need to transform the data 
so that it summarizes mean responses and it is in a format that allows for graphing in bar 
format. This means that we need to summarize and pivot the data in a long format. After we 
summarize and prep the data, we need to actually use ggplot to graph the data. For this reason,
we will break the task and create two seperate functions, and then apply those two functions
together to graph the information.

To begin, we will create a function that collapses and pivots the data. The function
has 4 arguments:
  1. df - specifies the data frame to be used,
  2. cols - is a list of the name of the columns we wish to include,
  3. labels - Labels of the responses
  4. - levels - Numeric values of the responses


*Note to reviewer, is there a way to add a vector of columns to the function instead of a 
range as currently specified. That way, the argument within pivot_longer cols will be a list
insead of a range. It might be that the columns are not in order so adding
a vector of columns would be better. However, I am having trouble making that happen. 

Anisha: I'm not sure I understand, what order would you like them to be? It looks like the correct order to me - strongly disagree, disagree, agree, strongly agree. You could also change to: cols = starts_with('q') to eliminate the need for the mincol and maxcol arguments altogether. Or if you really want the cols as an argument in the function, you could use: names(surveydf)[1:5]

```{r }

#Define the 
likertlevels <- c(1,2,3,4)
likertlabs <- c("Strongly disagree","Disagree","Agree","Strongly agree")
cols <- c(q1,q2,q3,q4,q5)

summ_likert <- function(df,mincol,maxcol,labels,levels) {
  df %>%
  pivot_longer(
    cols = {{mincol}}:{{maxcol}}, 
    names_to = "question",
    values_to = "frequency") %>%
  group_by(question,frequency) %>%
    count(name = "n_answers") %>%
  group_by(question) %>%
  mutate(percent_answers = (n_answers / sum(n_answers))*100,
         frequency = factor(frequency,
                           levels = levels,
                           labels = labels))
}

head(summ_likert(surveydf,q1,q5,labels,levels))
```


Next, we define a function to graph the data. The function has two arguments
  1. df - is the data frame,
  2. q_labels - Question labels (to be added and defined)

Note to reviewer: Still working on developing this visual.
```{r }
graph_likert <- function(df) {
  df %>%
  ggplot(aes(x = question,
             y = percent_answers,
             fill = frequency)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = abs(percent_answers)),
            position = position_stack(vjust = 0.5),
            color = "white",
            fontface = "bold") +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_viridis_d() +
  labs(title = "To what extent do you agree with the following statements?",
       x = "Percent of respondents",
       fill = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom")
}

```


## Apply the function

Lastly, we apply the function
```{r }
summ_likert(surveydf,q1,q5,labels,levels) %>%
  graph_likert()


```


 **Note to reviewer, the code below are notes to help develop the code, no need
to review/evaluate**





```{r, include = FALSE,evaluate = FALSE }
surveydf %>%
  pivot_longer(
    cols = c(q1,q2,q3,q4,q5),
    names_to = "question",
    values_to = "frequency"
  ) %>%
  group_by(question,frequency) %>%
    count(name = "n_answers") %>%
  group_by(question) %>%
  mutate(percent_answers = (n_answers / sum(n_answers))*100,
         frequency = factor(frequency,
                           levels = c(1,2,3,4),
                           labels = c("Strongly disagree","Disagree","Agree","Strongly agree"))) %>%
  mutate(percent_answers = if_else(frequency %in% c("Strongly disagree", "Disagree"), -percent_answers, percent_answers)
         )  %>%
  ggplot(aes(x = question,
             y = percent_answers,
             fill = frequency)) + 
  geom_col() +
  geom_text(aes(label = abs(percent_answers)),
            position = position_stack(vjust = 0.5),
            color = "white",
            fontface = "bold") +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_viridis_d() +
  labs(title = "To what extent do you agree with the following statements?",
       y = "Percent of respondents",
       fill = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom")

```


```{r, include = FALSE,evaluate = FALSE }
# Create sample graph
# survey_graph <- function(df,x,y) {
#  df %>%
#   pivot_longer(
#     cols = x:y,
#     names_to = "question",
#     values_to = "frequency"
#   ) %>%
#   group_by(question,frequency) %>%
#     count(name = "n_answers") %>%
#   group_by(question) %>%
#   mutate(percent_answers = (n_answers / sum(n_answers))*100,
#          frequency = factor(frequency,
#                            levels = c(1,2,3,4),
#                            labels = c("Strongly disagree","Disagree","Agree","Strongly agree"))) %>%
#   mutate(percent_answers = if_else(frequency %in% c("Strongly disagree", "Disagree"), -percent_answers, percent_answers)
#          )  %>%
#   ggplot(aes(x = question,
#              y = percent_answers,
#              fill = frequency)) + 
#   geom_col() +
#   geom_text(aes(label = abs(percent_answers)),
#             position = position_stack(vjust = 0.5),
#             color = "white",
#             fontface = "bold") +
#   coord_flip() +
#   scale_x_discrete() +
#   scale_fill_viridis_d() +
#   labs(title = "To what extent do you agree with the following statements?",
#        y = "Percent of respondents",
#        fill = NULL) +
#   theme_minimal() +
#   theme(axis.text.x = element_blank(),
#         axis.title.x = element_blank(),
#         panel.grid = element_blank(),
#         legend.position = "bottom")
# }
#   
# 
# survey_graph(surveydf,q1,q5)

```

